A Case Study in Preserving a High Energy Physics Application

### 2014-02-10 paper.tex
modify scripts

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1: Email\\ \hline
        \\
        1. Create a CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} https://github.com/cms-ttH/BEAN/blob/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://ekptrac.physik.uni-ka/... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \\ \hline
        Version 2: Script\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone https://github.com/cms-ttH/BEAN.git \\
        wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget http://pyyaml.org/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        version 3: Formulated Script \\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 4: Fine-Grained Toolkit\\ \hline
        \\
        \#description of OS version and hardware architecture \\
        \#list of indirect software dependencies \\
        \# set all environment variables\\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

@@

\subsubsection{Working principle of Packaging Utility}

@@

The shell script of the Solution 2 is simplified into one new version, which
only contains the necessary environment variables, access authority and the
actual analysis command. The Version 3 of Table~\ref{table:scripts} illustrates
the simplified script.

\subsubsection{Workflow of Packaging Utility}
\begin{figure*}
\centering
\epsfig{file=workflow-parrot.eps, height=4in, width=6.5in}
\caption{Workflow of Solution 4}
\label{fig:workflow-parrot}
\end{figure*}

@@

\subsubsection{Structure of Map File}

@@

\subsubsection{Discussion of Solution 4}

>>>>

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3\_11\_patch3 \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} https://github.com/cms-ttH/BEAN/blob/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://ekptrac.physik.uni-ka/... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone https://github.com/cms-ttH/BEAN.git \\
        wget -r http://nd.edu/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget http://pyyaml.org/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = (https://github.com) \\
        set {\bf PYYAML} = (http://pyyaml.org) \\
        set {\bf ND} = (http://nd.edu) \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        cvs co -r V03-09-23 PhysicsTools/PatUtils \\
        git clone \${\bf GIT}/cms-ttH/BEAN.git \\
        wget -r \${\bf ND}/~abrinke1/ElectronEffectiveArea.h \\
        scram b -j32 \\
        wget \${\bf PYYAML}/download/pyyaml/PyYAML...\\
        \#the experiment data is from HDFS \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\ 
        \hline
        {\bf Version 4: Fine-Grained Toolkit}\\ \hline
        \#deploy software environment using /archive \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        set {\bf GIT} = /archive/git \\
        set {\bf CMSSW} = /archive/CMSSW \\
        set {\bf HTTP} = /archive/http \\
        set {\bf EXP} = /archive/experiment\\
        set {\bf GRID} = /archive/grid-data \\
        cmsrel \$HOME/\$CMSSW\_BASE \\
        archive\_get \${\bf CMSSW}/...\\
        archive\_get \${\bf GIT}/cms-ttH/BEAN.git \\
        archive\_get \${\bf EXP}/nd.edu/~abrinke1/... \\        
        archive\_get \${\bf HTTP}/PyYAML/...\\
        archive\_get \${\bf GRID}/...\\
        scram b -j32 \\
        cmsenv\\
        python setup.py install --user \\
        scripts/roaster data/generic\_ttl.yaml \\
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        \\
        \#description of OS version and hardware architecture \\
        \#list of indirect software dependencies \\
        \# set all environment variables\\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\
        cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10\\
        cmsenv \\
        python setup.py install --user \\
        cd \$HOME/\$CMSSW\_BASE/src/ttH/TauRoast\\
        scripts/roaster data/generic\_ttl.yaml \\
        \\ \hline
    \end{tabular}
    \caption{Script of Fine-Grained Toolkit using Parrot}
    \label{table:parrot-script}
\end{table}

@@

\section{One Implemention of Fine-Grained Toolkit Using Parrot}
\subsection{Working principle of Packaging Utility}

@@

The shell script of the Solution 2 is simplified into one new version, which
only contains the necessary environment variables and the
actual analysis command. Table~\ref{table:parrot-script} illustrates
the simplified script.

\subsection{Workflow of Packaging Utility}
\begin{figure*}
\centering
\epsfig{file=workflow-parrot.eps, height=4in, width=6.5in}
\caption{Workflow of Solution 4}
\label{fig:workflow-parrot}
\end{figure*}

@@

\subsection{Structure of Map File}

@@

\subsection{Discussion of Solution 4}
